\begin{thebibliography}{99}
\itemsep=-1.2pt

\bibitem{Aichholzer-path}
\writer{O. Aichholzer}
{The path of a triangulation,}
{in: Proc.\ 15th Annual ACM Workshop Computational Geometry
(Miami Beach, Florida, June 13-15, 1999), ACM Press 1999, pp.~14-23.}

\bibitem{Aichholzer-WWW}
\writer{O. Aichholzer}
{Counting triangulations -- Olympics,}
{WWW page, created Oct.~5, 1999, last modified Nov.~20, 2001,
\url{http://www.cis.TUGraz.at/igi/oaich/triangulations/counting/counting.html}}

\bibitem{AignerZiegler}
\writer{M. Aigner and G. M. Ziegler}
{Proofs from THE BOOK,}
{Springer-Verlag Heidelberg, second ed. 2001.}


\bibitem{ACNS}
\writer{M. Ajtai, V. Chv\'atal, M. Newborn and E. Szemer\'edi}
{Crossing-free subgraphs,}
{{\sl Annals Discrete Math.} {\bf 12} (1982), 9-12.}

\bibitem{Anclin}
\writer{E. Anclin}
{An upper bound for the number of planar lattice triangulations},
{Preprint, TU Berlin 2002, 4~pages, ArXiv: \url{math.CO/0212140}.}

\bibitem{AvisFukuda}
\writer{D. Avis and K. Fukuda}
{Reverse search for enumeration,}
{{\sl Discrete Applied Math.} {\bf 65} (1996), 21-46.} 

\bibitem{Bespamyatnikh}
\writer{S. Bespamyatnikh}
{An efficient algorithm for enumeration of triangulations,}
{{\sl Comput. Geom.} {\bf 23} (2002),  271-279.} 

\bibitem{Behrends-MarkovChains}
\writer{E. Behrends}
{Introduction to Markov Chains, with Special Emphasis on Rapid Mixing,}
{Vieweg, Braunschweig/Wiesbaden 2000.}

\bibitem{4Marks}
\writer{M. de Berg, M. van Kreveld, M. Overmars, and O. Schwarzkopf}
{Computational Geometry. Algorithms and Applications,}
{Springer-Verlag, Heidelberg, second edition 2000.}

\bibitem{Dais-3dToric}
\writer{D. I. Dais}
{Resolving $3$-dimensional toric singularities,}
{{\sl S\'eminaires \& Congr\'es} {\bf 6}, Soc.\ Math.\ France, 2002,
155-186.}

\bibitem{DFNP91}
\writer{L. De Floriani, B. Falcidieno, G. Nagy, and C. Pienovi}
{On sorting triangles in a {D}elaunay tessellation},
{{\sl Algorithmica} , {\bf 6}, 1991, 522--532.}

\bibitem{DLRS}
\writer{J. De Loera, J. Rambau and F. Santos}
{Triangulations,}
{Book in preparation.}

\bibitem{Edelsbrunner92}
\writer{H. Edelsbrunner}
{An acyclicity theorem for cell complexes in $d$ dimension,}
{{\sl Combinatorica} {\bf 10} (1990), 251--260.}

\bibitem{FelsnerWernisch}
\writer{St.\ Felsner and L. Wernisch}
{Markov chains for linear extensions, the two-dimensional case,}
{in: Proc. Eighth Annual ACM-SIAM Symposium on Discrete Algorithms 
(New Orleans, LA, 1997), ACM, New York, 1997, 239--247.}

\bibitem{polymake}
\writer{E. Gawrilow and M. Joswig}
{polymake: an Approach to Modular Software Design in Computational Geometry,}
{Proceedings of the 17th Annual Symposium on Computational Geometry
(2001),
222--231;\\
Software package at \url{http://www.math.tu-berlin.de/polymake/},
version 1.5, September 2002.}

\bibitem{GKZ}
\writer{I.~M.~Gel'fand, M.~M.~Kapranov and A.~V.~Zelevinsky} 
{Discriminants, Resultants, and Multidimensional Determinants,}
{Birkh\"auser, Boston 1994.}

\bibitem{gmp}
\writer{GNU library for arbitrary precision arithmetic}
\url{http://www.swox.com/gmp/}

\bibitem{GoodmanPach}
\writer{J. E. Goodman and J. Pach}
{Cell decomposition of polytopes by bending,}
{{\sl Israel J. Math.} {\bf 64}, 1988, 129--138.}

\bibitem{Hastings}
\writer{R. E. Hastings}
{Triangulations of point configurations and polytopes,}
{Dissertation, Cornell University 1998, xii+103 pages,
\url{ftp://cam.cornell.edu/pub/theses/hastings.ps.gz}.}

\bibitem{JerrumSinclair}
\writer{M. Jerrum and A Sinclair}
{The {M}arkov Chain {M}onte {C}arlo Method: An Approach to Approximate Counting and Integration},
{in: Approximation Algorithms (D. Hochbaum, ed.), PWS Publishing, 482--520.}

\bibitem{KKMS}
\writer{G. Kempf, F. Knudsen, D. Mumford, and B. Saint-Donat}
{Toroidal Embeddings I,}
{{\sl Lecture Notes in Math.} {\bf 339}, Springer-Verlag 1973.}

\bibitem{Lee}
\writer{C. W. Lee}
{Subdivisions and triangulations of polytopes,}
{in: Handbook on ``Discrete and Computational Geometry''
(J. E. Goodman and J. O'Rourke, eds.),
CRC Press, Boca Raton FL 1997, 271--290.}

\bibitem{LW}
\writer{J. H. van Lint and R. M. Wilson}
{A Course in Combinatorics,}
{Cambridge University Press, Cambridge 1992; second edition 2001.}

\bibitem{Meyer}
\writer{S. Meyer}
{Enumeration von Triangulierungen,}
{Diplomarbeit, TU Berlin 2002, 87~Seiten.}

\bibitem{Orevkov}
\writer{S. Yu. Orevkov}
{Asymptotic number of triangulations with vertices in~${\mathbb Z}^2$,}
{{\sl J. Combinatorial Theory}, Ser.~A {\bf 86} (1999), 200-203.} 

\bibitem{PfeifleRambau}
\writer{J. Pfeifle and J. Rambau}
{Counting triangulations using oriented matroids,}
{to appear in: Algebra, Geometry, and Software Systems (M. Joswig and
  N. Takayama, eds.), Springer.}

\bibitem{Rambau-TOPCOM}
\writer{J. Rambau}
{TOPCOM --- Triangulations Of Point Configurations and Oriented Matroids,}
{to appear in 
Proc.\ Int.\ Cong.\ Mathematical Software ICMS 2002;\\
Software package at
\url{http://www.zib.de/rambau/TOPCOM/}, version 0.11.1, July 2002.}

\bibitem{SantosSeidel}
\writer{F. Santos and R. Seidel}
{A better upper bound on the number of triangulations of a planar point set,}
{to appear in: {\sl J. Comb. Theory Ser.~A}.}

\bibitem{StanleyEnumComb}
\writer{R. P. Stanley}
{Enumerative Combinatorics~I,}
{{\sl Cambridge Studies in Advanced Mathematics} {\bf 49},
 Cambridge University Press 1997.}

\bibitem{Sturmfels-GroePoly}
\writer{B. Sturmfels}
{Gr\"obner Bases and Convex Polytopes,}
{University Lecture Series, Vol.~8, Amer. Math.\ Soc.,
Providence, RI, 1995.}

\bibitem{Viro}
\writer{O. Ya.\ Viro}
{Real plane algebraic curves: Constructions with controlled topology,}
{{\sl Leningrad Math.\ J.} {\bf 1} (1990), 1059--1134.}

\bibitem{Zpoly}
\writer{G.~M.~Ziegler}
{Lectures on Polytopes,}
{{\sl Graduate Texts in Mathematics} {\bf 152}, 
Springer-Verlag New York 1995; revised edition, 1998.}

\end{thebibliography}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "bcc_ct"
%%% End:
